### 2020-12-03 doc/manuscript/Dow_manuscript.Rmd
rough work on discussion
@camerondow35 , this is quite different from what you had. (sorry!) Your text is all quite interesting and well-written, but I'd focus more on the themes in my text, as opposed to differences between ring- and diffuse-porous species. D'Orangeville et al covers those differences, and our novel contribution is the spring temperatures.

This still ndeds work, but hopefully helps. I'll do more when time allows.

## ("limitation in filling gap, how to interpret/fix")
Although the number of years analyzed here is limited (# years at SCBI, # years at HF), the signal is clear and consistent: for both species groups at both sites, warmer temperatures during virtually any part of the spring led to significantly earlier achievement of growth milestones (*CITE RELEVANT FIGS & TABLES* ).
This indicates that this is not a subtle effect.
However, the effect on L_PGS, r_max, and $\Delta DBH$, if any, is subtle, and a much longer record would be needed to detect such effects. 
Fortunately, we were able to get at annual growth using tree-ring data (Fig. `r tree_rings`).
These confirm that the effect of spring temperatures on annual growth is modest and generally not significant, while revealing a slightly more complex picture.
Although spring temperatures prior to May rarely had a significant influence on

## ("limitation in generalization, how to interpret/fix")

## ("contributions beyond")

@@

>>>>

## ("limitation in filling gap, how to interpret/fix")
Although the number of years analyzed here is limited (# years at SCBI, # years at HF), the signal is clear and consistent: for both species groups at both sites, warmer temperatures during virtually any part of the spring led to significantly earlier achievement of growth milestones (*CITE RELEVANT FIGS & TABLES* ).
This indicates that this is not a subtle effect.
However, the effect on L_PGS, r_max, and $\Delta DBH$, if any, is subtle, and a much longer record would be needed to detect such effects. 
Fortunately, we were able to get at annual growth using tree-ring data (Fig. `r tree_rings`).
These confirm that the effect of spring temperatures on annual growth is modest and generally not significant, while revealing a slightly more complex picture.
Although spring temperatures prior to May rarely had a significant influence on ...

## ("limitation in generalization, how to interpret/fix")
THe tree-rings also reveal that the strongest temperature sensitivity aligned with peak growing season.
This pattern is common across tree-ring studies in temperate deciduous forests.
(*1-2 sentences generalizing about climate sensitivity of temperate deciduous forest growth--Neil can do this most easily.*)
Thus, while our analysis is limited to two sites, we expect that the finding that spring temperatures have limited effect on annual tree grwoth will hold generall.y.

## ("contributions beyond")
Our findings contribute to a broader picture of the influence of spring temperatures on forest ecosystem function. 
Warm spring temperatures result in earlier leaf-out (REFS), an earlier start to net C sequestration (REFS), and--as shown here--earlier initiation of stem growth (*CITE RELEVANT FIGS & TABLES* ).
Yet, an earlier start to the growing season does not imply a longer growing season [Table `r hypotheses`, Figs `r pheno_Tsensitivity`, `r DOYtiming`;  @zani_increased_2020].
Rather, growth finishes sooner-- presumably because of *C sink limitation* [@zani_increased_2020].

@@

~~~~
